Typed Functional Genetic Programming

### 2013-06-23 tex/thesis.tex
[tex]

\begin{itemize}
	\item Constant or variable symbol $s$ is expression.
	\item Let there be a function with symbol $f$ which has $n$ arguments. 
	      And let there be expressions $e_{1}, ..., e_{n}$. 
	      Then ( $f$ $e_{1}$ ... $e_{n}$ ) is expression.   
\end{itemize}

@@

\begin{itemize}
	\item Terminal set $T$ : Set of symbols used as leaf nodes of program trees.
	\item Function set $F$ : Set of symbols used as internal nodes of program trees.
\end{itemize}

Therefore $building$ $blocks = T \cup F$.

>>>>

\begin{itemize}
	\item Constant\footnote{By constants we also mean procedures with zero  	
		  arguments.} or variable symbol $s$ is expression.
	\item Let there be a function with symbol $f$ which has $n$ arguments. 
	      And let there be expressions $e_{1}, ..., e_{n}$. 
	      Then ( $f$ $e_{1}$ ... $e_{n}$ ) is expression
	      \footnote{This notation comes from Lisp programming language, 
	      classical notation would be $f(e_{1}, ... ,e_{n})$. }.   
\end{itemize}

@@

\begin{itemize}
	\item Terminal set $T$ : Set of symbols used as leaf nodes of program trees 		
		  standing for constants and variables.
	\item Function set $F$ : Set of symbols used as internal nodes of program trees
	      standing for functions.
\end{itemize}

Therefore $building$ $blocks = T \cup F$.\\

%For brevity we will als

There is one important constrain on function implementations for functions from F:
There should be type $A$ that for every function symbol $f \in F$ the corresponding function implementation standing behind this symbol should be of a type 
$A \times ... \times A \rightarrow A$ and should be total (defined on all
combinations of inputs). And analogically for $t \in T$ being of a type A.

Satisfying this constrain ensures that every program tree build 
from $T \cup F$ will be total.

We can say that the motivation behind this work is to construct system where we
eliminate this constraint.

\subsection{Generating initial population}
We will describe tree generating method used by Koza in \cite{koza92} called
\textit{ramped half-and-half}.
